---
title: "Bay Area 511 Traffic"
author: "Kailin Lu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Description 

The Traffic Events API provides data about traffic incidences in the Bay Area. Incidences may be planned or un-planned. Examples of planned incidences include construction work or scheduled special events that involve road closures. 

Events contain a status which is either 'ACTIVE' if the incident is still occurring, or 'ARCHIVED' if it has concluded in the past. Filtering by 'ALL' will return both 'ACTIVE' and 'ARCHIVED' events. 

## Examples 

By default, the API will return events updated during the current day. The type of event can be found under `event_type`. 

```{r}
library(BayArea511r)
events <- traffic_events()
head(events)
```

Events returned can be filtered by fields such as event_type and the status 

```{r}
events_filtered <- traffic_events(status='ACTIVE', event_type='CONSTRUCTION')
head(events_filtered)
```





