---
title: "Bay Area 511 Transit Data"
author: "Kailin Lu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Description

Transit APIs describe the Bay Area's transit system operators, stops, announcements, and lines 

```{r}
library(BayArea511r)
```

## Operators

For a list of agencies currently operating in the Bay Area, use the `get_operators()`. 

```{r}
operators <- get_operators()
head(operators)
```

One useful column in the resulting DataFrame is the `id` column which gives the operator or agency ID. This ID can then be used as a filtering paramter for other API calls. 

Agencies which can be tracked real-time are those with `Monitored == TRUE`. 

## Stops 

Bay Area 511 provides two APIs which describe transit stop locations. The first which can be accessed using `get_stops()` is the more simple. The `id` column returned is the stop_id or stopCode which can be referenced as a filtering parameter in other transit APIs. 

```{r}
stops <- get_stops(operator_id='AC')
head(stops)
```

## Lines 

We can also retrieve the names of routes (lines) by operator ID 

```{r}
lines <- get_lines(operator_id='AC')
head(lines)
```
